# Set up the model profile

One of the first steps when building a new model with this framework is to set up the model profile, as it encapsulates all the dimensions that are handled in LOCA (LUCKINet overall computation algorithm).

This document is both, a tutorial to inform you about how to set up the profile, and a notebook that will set up a new profile with the information you provide for your new model run.


## Model dimensions

LOCA has the goal to build LUTS, the Land-Use Time-Series, a spatio-temporal allocation of various land surface concepts such as landcover, land use and crop types.


```{r}
authors <- list(cre = "Steffen Ehrmann")
```

This could additionally contain the fields `aut` and `ctb` for authors (people that wrote part of the code or compiled datasets) and contributors (people that contribute other than by authoring content)

```{r}
model_name <- "euroSandbox"
model_version <- "0.1.0"

my_license <- "https://www.gnu.org/licenses/gpl-3.0.txt"
```

```{r}
pixel_size <- c(0.008333333333333333218, 0.008333333333333333218)
```

```{r}
tile_size <- c(10, 10)
```

```{r}
model_extent <-  c(-31.26819, 40.21807, 27.63736, 82.5375)
```

```{r}
model_years <- c(2000:2020)
```

```{r}
model_domains <- list(crop = TRUE, livestock = FALSE, landuse = TRUE)
```



```{r}
par <- list(years = model_years,
            extent = model_extent,
            pixel_size = pixel_size,
            tile_size = tile_size,
            domain = model_domains)
```

```{r}
mdl_inputData <- list(directory = input_dir,
                      spatial = gadm360_path, geoscheme = geoscheme_path, 
                      raster_template = tmpl_pxls_path, 
                      model_mask = msk_mdlrgn_path)

mdl_ontology <- list(directory = onto_dir,
                     ontology = onto_path, gazetteer = gaz_path)

mdl_grids <- list(directory = grid_dir,
                  layers = c())

mdl_census <- list(directory = census_dir,
                   input = c(), output = c())

mdl_occurrence <- list(directory = occurr_dir,
                       input = c(), output = c())

mdl_suitability <- list(directory = suit_dir,
                        drivers = c(), output = map_suit_path)

mdl_initialLanduse <- list(directory = iniLand_dir,
                           input = c(), output = c())

mdl_allocation <- list(directory = alloc_dir,
                       input = c(), output = map_lusp_path)

mdl <- list(ontology = mdl_ontology,
            grid_data = mdl_grids,
            census_data = mdl_census,
            occurrence_data = mdl_occurrence,
            suitability_maps = mdl_suitability,
            initial_landuse_map = mdl_initialLanduse,
            allocation_maps = mdl_allocation)
```

```{r}
.write_profile(name = model_name,
               version = model_version,
               authors = authors,
               license = my_license,
               parameters = par,
               modules = mdl)

# and create the profile path
profile_path <- paste0(work_dir, model_name, "_", model_version, ".RData")
```

This also creates the directory `~/work_dir/name_version` that will contain all the temporary data items and the file `~/work_dir/name_version.RData` that contains the profile information.


```{r}
# lc_limits <- tibble(landcover = rep(c("Cropland_lc", "Forest_lc", "Meadow_lc", "Other_lc"), each = 4),
#                     lcID = rep(c(10, 20, 30, 40), each = 4),
#                     luckinetID = as.character(rep(c(1120, 1122, 1124, 1126), 4)),
#                     short = rep(c("crop", "forest", "grazing", "other"), 4),
#                     min = c(0.5, 0, 0, 0, 0, 0.5, 0, 0, 0, 0, 0.5, 0, 0, 0, 0, 0),
#                     max = c(1, 0.5, 0.5, 0.5, 0.5, 1, 0.5, 0.5, 0.5, 0.5, 1, 0.5, 0, 0, 0, 1))

# covNames <- c(
#   "meElevation_30as/elevationMeanLand",
#   "iGHS_POP/GHSP",
#   "CHELSA_tClimate/yearMax",
#   "CHELSA_tClimate/yearMin",
#   "CHELSA_tClimate/yearMean",
#   "CHELSA_pClimate/drySeasonLength",
#   "CHELSA_pClimate/yearTotal",
#   "CHELSA_pClimate/yearMin",
#   "CHELSA_pClimate/yearMax",
#   "travelTime/travelTime",
#   "soilMap/soilDepthMean",
#   "CCI_landCover_agg/forest",
#   "CCI_landCover_agg/grassland",
#   "CCI_landCover_agg/shrubland",
#   "CCI_landCover_agg/agriculture",
#   "iGSW_30as/permanent",
#   "iGSW_30as/seasonal",
#   "linearDistance_30as/coastalFlats",
#   "linearDistance_30as/reservoirs",
#   "linearDistance_30as/river",
#   "linearDistance_30as/ocean",
#   "linearDistance_30as/lake"
# )
```
